Towards a Mechanized Proof of Noninterference

### 2013-12-18 paper/paper.tex
capital C Coq.  A specific Coq, not just any old coq.

In this paper, we present a simple information flow typed language \langName,
prove noninterference for the language, and discuss our experiences beginning to
mechanize this proof in coq.  Although we did not complete our proof, we were
able to catch inaccuracies and subtleties that the proof we based our approach
on did not handle or explicitly cover.  This is the first step towards a
verified compiler for a language with information flow types such as Jif or
FlowCaml, which allows for a more trustworthy compiler and language definition,
by allowing users to verify the proofs in a proof assistant like Coq.  As far as
we know, a verified proof of noninterference for such a language has not been
implemented, let alone a verified compiler.  We are confident that, given more
time and a large amount of work, such a verified compiler could be realized for
a mature information flow language.

>>>>

In this paper, we present a simple information flow typed language \langName,
prove noninterference for the language, and discuss our experiences beginning to
mechanize this proof in Coq.  Although we did not complete our proof, we were
able to catch inaccuracies and subtleties that the proof we based our approach
on did not handle or explicitly cover.  This is the first step towards a
verified compiler for a language with information flow types such as Jif or
FlowCaml, which allows for a more trustworthy compiler and language definition,
by allowing users to verify the proofs in a proof assistant like Coq.  As far as
we know, a verified proof of noninterference for such a language has not been
implemented, let alone a verified compiler.  We are confident that, given more
time and a large amount of work, such a verified compiler could be realized for
a mature information flow language.
